Is anchoring better?

### 2022-05-25 manuscript/abstract.tex
Autocommit
Working on BMB's feedback

In many applications which use generalized linear (mixed) models, outcome predictions or predicted probabilities are often of interest. For models that involve complex multiplicative interactions, additional non-focal predictors or nonlinear link functions, the estimated coefficient are not readily interpretable. A general way to summarize these kind of models is through predictions, which are not only dependent on choice of representative values of focal predictor but also sensitive to which values of non-focal predictors are chosen. The most common approach is generating predictions at a ``reference point'', usually the mean, of non-focal predictor, i.e., mean-based (centered) which could be considered as the effect of an ``average case'' in the population. In the presence of sources of bias such as additional non-focal predictors, nonlinear link functions, random effect terms, etc., mean-based approach generate predictor effects that are biased and may not be consistent with the observed quantities. An alternative is the whole-sample-based approach which estimates the average effect in the population. Moreover, anchored effects provide an alternative and a more clear way to describe uncertainty associated with the focal predictor of interest. In addition to theoretical and methodical comparison, using simulation, we illustrate the two approaches and show that they can produce substantially different results and that whole-sample-based approach can not only produce estimates consistent with the observed values, but also appropriate for bias correction. We also present an alternative way, anchored confidence intervals, to describe uncertainties associated with these predictions.

@@

>>>>

In applications that use generalized linear (mixed) models, outcome predictions are often of interest. For models that involve complex multiplicative interactions, additional non-focal predictors or nonlinear link functions, the estimated coefficients are not readily interpretable. A general way to summarize these kind of models is through predictions, that depend not only on choice of representative values of focal predictor but are also sensitive to which values of non-focal predictors are chosen. The most common approach is generating predictions at a reference point, usually the mean, of non-focal predictor, i.e., mean-based (centered) which could be considered as the effect of an average case in the population. In the presence of additional non-focal predictors, nonlinear link functions, random effect terms, etc., mean-based approach generate predictions that are biased and may not be consistent with the observed quantities. An alternative is the whole-sample-based approach which estimates the average effect in the population. Moreover, anchored effects provide an alternative and a more clear way to describe uncertainty associated with the focal predictor of interest. In addition to theoretical and methodical comparison, using simulation, we illustrate the two approaches and show that they can produce substantially different results and that whole-sample-based approach can not only produce estimates consistent with the observed values, but also appropriate for bias correction. We also present an alternative way, anchored confidence intervals, to describe uncertainties associated with these predictions.

@@

\fix
